Quantum Magic Games

### 2023-07-06 paper/main.tex
paper => conclusion

\maketitle
\begin{abstract}
This paper explores the phenomenon of quantum pseudo-telepathy, a form of communication that exhibits properties resembling telepathy by leveraging aspects of the quantum realm. Specifically, the focus is on the Mermin-Peres magic square game, which exemplifies quantum pseudo-telepathy and provides a simplified proof for the Kochen-Specker theorem. The paper begins by discussing various examples of quantum pseudo-telepathy games and their incompatibility with classical winning strategies, highlighting the necessity of prior entanglement between players. Additionally, it delves into the intricacies of the magic square game, classical approaches, the impossibility of consistent classical winning, and the rationale behind the successful implementation of a quantum strategy. Moreover, it explores the connection between the game and the proof of the incompatibility of noncontextual hidden-variable theories. Furthermore, a generalization of games similar to the magic square, proposed by Arkhipov, is presented. Ultimately, through this investigation, the paper sheds light on the fascinating realm of quantum pseudo-telepathy and its implications for our understanding of classical physics and quantum mechanics.
\end{abstract}

@@

\paragraph{Outline of this paper.}
In Section~\ref{sec:magic-square}, we detail the intrinsics of the
magic square game, classical approaches and why it is impossible to
systematically win the game classically, how and why the quantum
strategy works, and how to implement it. We also briefly discuss how
the game translates to the proof of incompatibility of a
noncontextual hidden-variable theory. Then, in
Section~\ref{sec:extending}, we describe a generalization of games
that follow the same style of the magic square game, given
by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes this report.

@@

As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
called this way because, under classical assumptions, there is no such
a square: it is impossible to construct a \(3 \times 3\) matrix filled
with \(\pm 1\)'s, with the constraints that the product of every row
is \(+1\) and the product of every column is \(-1\). We can, however,
construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
the \(3 \times 3\) grid that Alice and Bob can use to win the magic
square game systematically.  Notice that the eigenvalues of the
observables at each cell are \(\pm 1\). Furthermore, the product of
every row is \(+I\) and the product of every column is \(-I\).  The
quantum strategy works as follows: Alice measures all the observables
from the \(i\)-th row of the predefined matrix. She fills each cell
with the result of each measurement. Similarly, Bob measures all the
observables in the \(j\)-th column that was assigned to him, and fills
each of his cells with the outcomes of each measurement. (It is worth
to point out that the order of their measurements is not important.)
Example~\ref{ex:quantum-sol} depicts a round of the game.

@@

  \begin{theorem}[The Mermin-Peres Magic Square Game Is Winnable]
    \label{theo:quantum-wins}
    There exists a quantum strategy for the Mermin-Peres magic square
    game, which consists of allowing Alice and Bob to exchange
    entangled qubits \emph{before} the game begins, that wins with
    certainty every round.
  \end{theorem}
\end{proof}

>>>>

\maketitle
\begin{abstract}
  \textbf{TODO}
\end{abstract}

@@

\paragraph{Outline of this paper.}
In Section~\ref{sec:magic-square}, we detail the intrinsics of the
magic square game, classical approaches and why it is impossible to
systematically win the game classically, how and why the quantum
strategy works, and how to implement it. We also briefly discuss how
the game translates to the proof of incompatibility of a
noncontextual hidden-variable theory. Then, in
Section~\ref{sec:extending}, we describe a generalization of games
that follow the same style of the magic square game, given
by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes the
presentation.

@@

As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
called this way because, under classical assumptions, there is no such
a square: it is impossible to construct a \(3 \times 3\) matrix filled
with \(\pm 1\)'s, with the constraints that the product of every row
is \(+1\) and the product of every column is \(-1\). We can, however,
construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
the \(3 \times 3\) grid that Alice and Bob can use to win the magic
square game systematically.  Notice that the eigenvalues of the
observables at each cell are \(\pm 1\). Furthermore, the product of
every row is \(+I\) and the product of every column is \(-I\).  The
quantum strategy works as follows: Alice measures all the observables
from the \(i\)-th row of the predefined matrix. She fills each cell
with the result of each measurement. Similarly, Bob measures all the
observables in the \(j\)-th column that was assigned to him, and fills
each of his cells with the outcomes of each
measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.

@@

  \begin{theorem}[The Mermin-Peres Magic Square Game Is Winnable]
    \label{theo:quantum-wins}
    There exists a quantum strategy for the Mermin-Peres magic square
    game, which consists of allowing Alice and Bob exchanging
    entangled qubits \emph{before} the game begins, that wins with
    certainty every round.
  \end{theorem}
\end{proof}
